Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-26 mu/article/article.tex
Up V^a at half description.

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

@@

150$^{\circ}$ is the zone of the absolute maximum response for both,

@@

\textcolor{red}{
Also there is another zone of interest for energies from 0.70\,eV to 0.74\,eV
}

@@

$\mathcal{V}^{\mathrm{yz}}$ components for the fixed polarization angle.

@@

see that for the energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and

@@

@@

% %%%%%%%%%%%%%%%%%
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\end{figure}
\begin{figure}[b]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone of the absolute maximum response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
% 
Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
% %%%%%%%%%%%%%%%%
% %% Starting description of ALT |V^{a}|, components and RTP
% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %%        alt-plots/alt-3d-vab.gp
% %%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-2}
\end{figure}
\textcolor{red}{
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha = 40^{\circ}$. In the top frames of Figs. 
%
\ref{fig:up-vab-comp-rtp-1}  and \ref{fig:up-vab-comp-rtp-2} we present the
results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing
the polarization angle to $40^{\circ}$ for the \emph{up} structure vs the photon
energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles for
the energy range from 0.0\,eV to 0.16\,eV and from 
}

>>>>

\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}
% 
\begin{table}[t]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

@@

@@

@@

150$^{\circ}$ is the zone of the maximum response for both,

@@

@@

$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $145^{\circ}$.

@@

see that for the energy range from 0.70\,eV to 0.75\,eV all the $xx$, $xy$, and

@@

Also there is another zone of interest for energies from 0.70\,eV to 0.75\,eV

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\begin{figure}[t]
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
% %% 0.0 eV - 0.16 eV
% %% Starting description of UP |V^{a}|, components and RTP
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone of the maximum response for both,
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is 0.088\,eV. 
\ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vy-comp-rtp-1} we present the results
polarization angle to $40^{\circ}$ for the \emph{up} structure vs photon energy
and the corresponding polar $\varphi$ and azimuthal $\theta$ angles. In the
bottom frames of Figs. \ref{fig:up-vx-comp-rtp-1} and \ref{fig:up-vx-comp-rtp-1}
we present the decomposition of $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, $\mathcal{V}^{\mathrm{xz}}$ and
$\mathcal{V}^{\mathrm{yz}}$ components with $\alpha$ fixed to $40^{\circ}$. From
Fig. \ref{fig:up-vx-comp-rtp-1} we have that for an incoming bean with energy of
0.088\,eV the three components have similar contributions and have values of
$\mathcal{V}^{\mathrm{xx}}= -36.5$\,Km/s,
$\mathcal{V}^{\mathrm{xy}}=-23.2$\,Km/s, and
$\mathcal{V}^{\mathrm{xz}}=39.8$\,Km/s resulting in a value of
$|\mathcal{V}^{\mathrm{x}}|=58.7$\,Km/s and corresponding to polar and azimuthal
angles of $\varphi=47.4$ and $\theta=212.5$, respectively. Also we found that. Now, from Fig.
\ref{fig:up-vy-comp-rtp-1} we have that for the same incoming beam energy the
$yx$ and $yy$ components have less contributions for the total response than the
$yz$ having values of $\mathcal{V}^{\mathrm{yx}}= -7.9$\,Km/s
$\mathcal{V}^{\mathrm{yy}}=  8.5$\,Km/s $\mathcal{V}^{\mathrm{yz}}= 87.1$\,Km/s
and resulting in a value of the total response of
$|\mathcal{V}^{\mathrm{y}}|=87.9$\,Km/s with polar and azimuthal angles
$\varphi=7.6$ $\theta=132.6$, respectively.
\begin{figure}[t]
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\begin{figure}[t]
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-2}
Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
% %% Starting description of UP |V^{a}|, components and RTP
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha = 40^{\circ}$. In the top frames of Figs. 
\ref{fig:up-vab-comp-rtp-1}  and \ref{fig:up-vab-comp-rtp-2} we present the
results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing
the polarization angle to $40^{\circ}$ for the \emph{up} structure vs the photon
energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles for
the energy range from 0.0\,eV to 0.16\,eV and from
